The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-29 manuscript/manuscript.Rnw
cite the NWM grant

  \section*{Funding}
  Partial support for this research came from the \textit{Eunice
    Kennedy Shriver} National Institute of Child Health and Human
  Development (NICHD), National Institutes of Health, U.S. Department
  of Health and Human Services (N01-HD-3342), and the National Science
  Foundation BCS-0827546.

@@

>>>>

  \section*{Funding}
  Partial support for this research came from the \textit{Eunice
    Kennedy Shriver} National Institute of Child Health and Human
  Development (NICHD), National Institutes of Health, U.S. Department
  of Health and Human Services (N01-HD-3342), the National Science
  Foundation (BCS-0827546 and BCS-0751508), and a seed grant from the
  Institute for Genomic Biology at the University of Illinois,
  Urbana-Champaign.

@@

  \DLA{Unclear what the IGB grant is; Derek: which grant did you want
    me to cite? Mentioned seed grant.}
